### 2018-06-13 dissemination.publication/request-asplos18-front-matter/paper.tex
added one more bullet point
updated TOC

\item collaborating with the community, our Advisory Board and ACM to address the above issues;
\item using the ReQuEST experience to assist AE at the upcoming \href{http://sysml.cc}{SysML'19} conference;
\item replacing non-representative benchmarks with realistic workloads;
\item creating realistic training sets based on mispredictions shared by the community;
\item improving the benchmarking and co-design methodology, and contributing to emerging benchmarking initiatives such as \href{http://mlperf.org}{MLPerf};
\item collaborating with other competitions such as \href{https://rebootingcomputing.ieee.org/lpirc}{LPIRC}, \href{https://dawn.cs.stanford.edu/benchmark}{DAWNBench} and \href{https://sc18.supercomputing.org/experience/studentssc/student-cluster-competition}{SCC} on developing a common experimental framework;
\item standardizing \href{http://cKnowledge.org/rpi-crowd-tuning}{multi-objective autotuning and co-design workflows};
\item improving and documenting the experimental framework and scoreboard;
\item generating reproducible and interactive reports (see examples \href{http://cknowledge.org/repo/web.php?wcid=report:request-overview}{1} and \href{http://cKnowledge.org/rpi-crowd-tuning}{2});
\item adding new shared components such as workloads, data sets, tools and platforms;
\item automating AE "at the source" by integrating CK workflows with e.g.\ \href{https://hotcrp.com/}{HotCRP};
\item standardizing APIs and meta-descriptions of shared components to make them "marketplace-ready";
\item running new ReQuEST competitions for other workloads!

@@

  \textbf{Optimizing Deep Learning Workloads on Arm GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\

@@

  \textbf{Leveraging the VTA-TVM Hardware-Software Stack for FPGA Acceleration of 8-bit ResNet-18 Inference}\newline\newline{Thierry Moreau}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229766}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229772}{Artifact DOI}~] [~\href{https://github.com/uwsaml/vta}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-resnet-tvm-fpga}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-resnet-tvm-fpga}{CK results}~]\newline &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_functional_dl.jpg}\end{center} &  ~ &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\

>>>>

\item collaborating with the community, our Advisory Board and ACM to address the above issues;
\item using the ReQuEST experience to assist AE at the upcoming \href{http://sysml.cc}{SysML'19} conference;
\item replacing non-representative benchmarks with realistic workloads;
\item creating realistic training sets based on mispredictions shared by the community;
\item improving the benchmarking and co-design methodology, and contributing to emerging benchmarking initiatives such as \href{http://mlperf.org}{MLPerf};
\item collaborating with other competitions such as \href{https://rebootingcomputing.ieee.org/lpirc}{LPIRC}, \href{https://dawn.cs.stanford.edu/benchmark}{DAWNBench} and \href{https://sc18.supercomputing.org/experience/studentssc/student-cluster-competition}{SCC} on developing a common experimental framework;
\item standardizing \href{http://cKnowledge.org/rpi-crowd-tuning}{multi-objective autotuning and co-design workflows};
\item extending unified collection of platform information in CK;
\item improving and documenting the experimental framework and scoreboard;
\item generating reproducible and interactive reports (see examples \href{http://cknowledge.org/repo/web.php?wcid=report:request-overview}{1} and \href{http://cKnowledge.org/rpi-crowd-tuning}{2});
\item adding new shared components such as workloads, data sets, tools and platforms;
\item automating AE "at the source" by integrating CK workflows with e.g.\ \href{https://hotcrp.com/}{HotCRP};
\item standardizing APIs and meta-descriptions of shared components to make them "marketplace-ready";
\item running new ReQuEST competitions for other workloads!

@@

  \textbf{Optimizing Deep Learning Workloads on ARM GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\

@@

  \textbf{Leveraging the VTA-TVM Hardware-Software Stack for FPGA Acceleration of 8-bit ResNet-18 Inference}\newline\newline{Thierry Moreau, Tianqi Chen, Luis Ceze}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229766}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229772}{Artifact DOI}~] [~\href{https://github.com/uwsaml/vta}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-resnet-tvm-fpga}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-resnet-tvm-fpga}{CK results}~]\newline &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_functional_dl.jpg}\end{center} &  ~ &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
